Notes on Wide Gap

### 2016-04-18 paper/wide_gap_notes.tex
time needs delta too to come in at same order
Bphi thin gap reduction
uphi thin gap reduction
notebooks for wide gap equations

\begin{multline}
\frac{1}{r}\partial_t \left(\nabla^2 \Psi - \frac{2}{r} \partial_r \Psi \right) + J\left(\Psi, \frac{1}{r^2} \left( \nabla^2 \Psi - \frac{2}{r} \partial_r\Psi\right) \right) - \frac{1}{r} 2 u_\phi \partial_z u_\phi \\
= J\left(A, \frac{1}{r^2} \left( \nabla^2 A - \frac{2}{r} \partial_rA\right) \right) - \frac{2}{r}B_\phi \partial_z B_\phi \\
+ \frac{1}{\reye} \left[ \nabla^2 \left(\frac{1}{r} \nabla^2 \Psi\right) - \frac{1}{r^3} \partial_r^2 \Psi - \frac{1}{r^4}\partial_r\Psi\right]
\end{multline}

@@

The $A$ equation reduces as follows.

@@

\beq
\partial_t A = (1 - \delta x)\delta^{-2} J(A, \Psi) + \frac{1}{\reym} \left[(1 - \delta x) \delta^{-2} \left(\partial_x^2 A + \delta\partial_x A + \delta x \partial_x^2 A \right) + \delta^{-2} \partial_z^2 A - \frac{2}{\delta}(1 - \delta x) \partial_x A \right]
\eeq

@@

which is the (unperturbed) thin-gap equation, when we drop all terms that are higher order than $\delta^{-2}$. Note that this means we have to drop terms of $\mathcal{O}(\delta^{-1})$, which means that this formalism cannot be applied to the perturbed equations (see Equation \ref{eq:A_perturbed}), because the term $B_0\partial_zA$ would drop out, but shouldn't. I'm also not sure how the $\partial_t$ term formally picks up a $\delta^{-2}$...?

>>>>

\begin{multline}
\label{eq:Psi_unperturbed}
\frac{1}{r}\partial_t \left(\nabla^2 \Psi - \frac{2}{r} \partial_r \Psi \right) + J\left(\Psi, \frac{1}{r^2} \left( \nabla^2 \Psi - \frac{2}{r} \partial_r\Psi\right) \right) - \frac{1}{r} 2 u_\phi \partial_z u_\phi \\
= J\left(A, \frac{1}{r^2} \left( \nabla^2 A - \frac{2}{r} \partial_rA\right) \right) - \frac{2}{r}B_\phi \partial_z B_\phi \\
+ \frac{1}{\reye} \left[ \nabla^2 \left(\frac{1}{r} \nabla^2 \Psi\right) - \frac{1}{r^3} \partial_r^2 \Psi - \frac{1}{r^4}\partial_r\Psi\right]
\end{multline}

@@

The $u_\phi$ equation (Equation \ref{eq:uy}) reduces as follows:
\begin{equation}
\partial_t \uphi + \frac{J(\psi, \uphi)}{r} + \frac{\uphi \partial_z \psi}{r^2} = \frac{J(A, B_\phi)}{r} + \frac{B_\phi \partial_z A}{r^2} + \nu \left( \nabla^2 \uphi - \frac{\uphi}{r}\right)
\end{equation}

\beq
\begin{split}
& \delta^{-2} \partial_t u_\phi + (1 - \delta r)\delta^{-2} J(\Psi, u_\phi) + (1 - 2\delta r)\delta^{-1} u_\phi \partial_z \Psi  = \\
& (1 - \delta r)\delta^{-2} J(A, B_\phi) + (1 - 2\delta r)\delta^{-1} B_\phi \partial_z A + \\
& \nu \left[(1 - \delta x) \delta^{-2} \left(\partial_x^2 u_\phi + \delta \partial_x u_\phi + \delta x \partial_x^2 u_\phi \right) + \delta^{-2} \partial_z^2 u_\phi \right] - \nu(1 - \delta r) u_\phi
\end{split}
\eeq

\beq
\partial_t u_\phi + J(\Psi, u_\phi) = J(A, B_\phi) + \nu(\partial_x^2 u_\phi + \partial_z^2 u_\phi)
\eeq

The $A$ equation reduces as follows. We also choose $\widetilde{t} = \delta^2 \Omega_0 t$ so that time comes in at the same order as the other dimensions...

@@

\beq
\delta^{-2} \partial_t A = (1 - \delta x)\delta^{-2} J(A, \Psi) + \frac{1}{\reym} \left[(1 - \delta x) \delta^{-2} \left(\partial_x^2 A + \delta\partial_x A + \delta x \partial_x^2 A \right) + \delta^{-2} \partial_z^2 A - \frac{2}{\delta}(1 - \delta x) \partial_x A \right]
\eeq

@@

which is the (unperturbed) thin-gap equation, when we drop all terms that are higher order than $\delta^{-2}$. Note that this means we have to drop terms of $\mathcal{O}(\delta^{-1})$, which means that this formalism cannot be applied to the perturbed equations (see Equation \ref{eq:A_perturbed}), because the term $B_0\partial_zA$ would drop out, but shouldn't. (??)

The $B_\phi$ equation
\begin{multline}
\partial_t B_\phi = \frac{1}{r} J(A, \uphi) + \frac{1}{r} J(B_\phi, \psi)\\
+ \frac{1}{r^2} B_\phi \partial_z \psi - \frac{1}{r^2} \uphi \partial_z A + \eta \left(\nabla^2 B_\phi - \frac{1}{r^2} B_\phi \right)
\end{multline}

\beq
\begin{split}
\delta^{-2} \partial_t B_\phi  & = (1 - \delta r) \delta^{-2} J(A, u_\phi) + (1 - \delta r) \delta^{-2} J(B_\phi, \Psi) \\
& + (1 - 2 \delta r) \delta^{-1} B_\phi \partial_z \Psi - (1 - 2 \delta r) \delta^{-1} u_\phi \partial_z A + \\
& \eta\left[(1 - \delta x) \delta^{-2} \left(\partial_x^2 B_\phi + \delta \partial_x B_\phi + \delta x \partial_x^2 B_\phi \right) + \delta^{-2} \partial_z^2 B_\phi\right] - \eta (1 - 2\delta r) B_\phi
\end{split}
\eeq

\beq
\partial_t B_\phi = J(A, u_\phi) + J(B_\phi, \Psi) + \eta(\partial_x^2 B_\phi + \partial_z^2 B_\phi)
\eeq

The $\Psi$ equation (Equation \ref{eq:Psi_unperturbed}) reduces as follows

\beq
\begin{split}
& (1 - \delta x) \delta^{-2} \left[(1 - \delta x) \delta^{-2} \left(\partial_x^2 \Psi + \delta \partial_x \Psi + \delta x \partial_x^2 \Psi \right) + \delta^{-2} \partial_z^2 \Psi - 2(1 - \delta x)\delta^{-1}\partial_x \Psi \right] \\
& + \delta^{-2} J(\Psi, (1-2\delta x)\left((1 - \delta x) \delta^{-2} \left(\partial_x^2 \Psi + \delta \partial_x \Psi + \delta x \partial_x^2 \Psi \right) + \delta^{-2} \partial_z^2 \Psi - 2(1 - \delta x)\delta^{-1}\partial_x \Psi \right)) \\
& - (1 - \delta x)2\delta^{-1} u_\phi \partial_z u_\phi \\
& = \delta^{-2} J(A, (1 - 2 \delta)\left((1 - \delta x) \delta^{-2} \left(\partial_x^2 \Psi + \delta \partial_x \Psi + \delta x \partial_x^2 \Psi \right) + \delta^{-2} \partial_z^2 \Psi - 2(1 - \delta x) \delta^{-1} A \right)) \\
& - 2(1 - \delta x)\delta^{-1} B_\phi \partial_z B_\phi + \frac{1}{\reye} \left[\delta^{-2}(\partial_x^2 + \delta \partial_x + \delta x \partial_x^2 + \partial_z^2)((1 - \delta x)(\partial_x^2\Psi + \delta \partial_x\Psi + \delta x \partial_x^2\Psi + \partial_z^2\Psi))\right] \\
& + \frac{1}{\reye}\left[(1 - 3\delta x)\delta^{-2} \partial_x^2 \Psi - (1 - 4 \delta x)\delta^{-1}\partial_x \Psi \right]
\end{split}
\eeq

The viscous term is

\beq
\frac{1}{\reye} (1 - 
\eeq
